Re-Allocation of Resources during Releases \titlenote{Copyright note}

### 2013-12-17 paper1/latex/paper1.tex
tarted working on reviews from Peter.

From release ``linuxv2.6.13'' to ``linuxv3.11'' We examine the contribution in writing code by the developers to understand the behavior during the two vital segments in a release cycle. Figure 8 plots the cumulative representation of the percentage of working with owned files ($\omega$\textit{MP}) during the development period and the percentage of working with owned files ($\omega$\textit{RP}) during release period of ``linuxv2.6.13''. From the figure It can be observed that with the increase of every 10 files that developers working in, $\omega$\textit{RP} is going down apart from the line of $\omega$\textit{MP}. Up to a certain number may be around 2200 files developers mostly work with owned files. We see the similar picture for other releases too.
\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3.4in]{cumulFileOwnP.png}
\caption{\small \sl Cumulative percentage of working with owned files in DP and RP of release 2.3.13}
\end{center}
\end{figure}

>>>>

From release ``linuxv2.6.13'' to ``linuxv3.11'' We examine the contribution in writing code by the developers to understand the behavior during the two vital segments in a release cycle. Figure 8 plots the cumulative representation of the percentage of working with owned files ($\omega$\textit{MP}) during the development period and the percentage of working with owned files ($\omega$\textit{RP}) during release period of ``linuxv2.6.13''. From the figure it can be observed that with the increase of every 10 files that developers working in, $\omega$\textit{RP} is going down apart from the line of $\omega$\textit{MP}. Up to a certain number may be around 2200 files developers mostly work with owned files. We see the similar picture for other releases too.
\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3.4in]{cumulFileOwnP.png}
\caption{\small \sl Cumulative percentage of working with owned files in DP and RP of release 2.3.13}
\end{center}
\end{figure}
